Determinants of Wage Variation in Canada

### 2024-11-26 paper/paper.qmd
update scripts and readme

## Estimand

@@

This section aims to offer an insightful understanding of the dataset utilized in our analysis, which serves as the foundation for our examination of the relationship between education and average hourly wage rates in Canada, specifically within the 25-54 age demographic.

>>>>

@@

This section aims to offer a understanding of the dataset utilized in our analysis, which serves as the foundation for our examination of the relationship between education and average hourly wage rates in Canada, specifically within the 25-54 age demographic.
